Local PCA Shows How Population Structure Differs Along the Genome

### 2016-04-13 writeup/local_pca_paper.tex
corrected local pca bit

A number of methods for dimensionality reduction also use a strategy of ``local PCA''
\citep[e.g.][]{manjon2013diffusion,kambhatla1997dimension,weingessel2000local,roweis2000nonlinear},
performing PCA not on the entire dataset but instead on subsets,
providing ``local'' pictures which are then stitched back together to give a global picture.
Our method shares this common thread, but differs somewhat in the context and goals,
and future methods may benefit from this substantial literature \citep[reviewed in][]{vandermaaten2009dimensionality}.

>>>>

A number of methods for dimensionality reduction also use a strategy of ``local PCA''
\citep[e.g.][]{manjon2013diffusion,kambhatla1997dimension,weingessel2000local,roweis2000nonlinear},
performing PCA not on the entire dataset but instead on subsets,
providing ``local'' pictures which are then stitched back together to give a global picture.
This differs from our use of the term in that we restrict to subsets of \emph{variables} instead of subsets of observations.
Future methods for visualization of genomic data
may benefit from other advances in this substantial literature \citep[reviewed in][]{vandermaaten2009dimensionality}.
